A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-12 implementation.tex
Fix implementation

Product materialisation is the final piece of the puzzle. In the current
implementation we put off computing intermediate products until six transition
variables of one of the automata is known to be either \Fudge{present or absent}. The
number was chosen experimentally. The other automaton for the product is
selected randomly.

% this is unclear; don't we delay computing products until one of the
% automata is (almost) completely defined?

>>>>

Product materialisation is the final piece of the puzzle. In the current
implementation we put off computing intermediate products until at most six transition
variables of one of the automata are not known to always be used ($> 0$) or always unused ($\leq 0$). The
number was chosen experimentally. The other automaton for the product is
selected randomly.
